Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-11-13 paper/tex/discussion.tex
elaborated on true PDFs

Section~\ref{sec:metrics} discussed the difficulty in evaluating PDF accuracy for individual objects.
In a follow-up study, we will
 % use generative adversarial networks\citep[(GANs)][]{Goodfellow:14} trained on the simulation data to
generate ``true PDF'' distributions, yielding a dataset that enables a test of PDF accuracy for individual galaxies rather than solely ensembles.

>>>>

Section~\ref{sec:metrics} discussed the difficulty in evaluating PDF accuracy for individual objects with known $(z, d)$ information but without a known $p(z, d)$.
In a follow-up study, we will
 % use generative adversarial networks\citep[(GANs)][]{Goodfellow:14} trained on the simulation data to
generate mock data probabilistically, yielding true PDFs in addition to true redshifts and photometric data.
This future data set will enable tests of PDF accuracy for individual galaxies rather than solely ensembles.
